Data Preparation

### 2019-02-28 Data Preparation.Rmd
d_course saved in pillar1 data

# Save Data
```{r}
save(d_course, lists, d_AoD, d_assessment, d_ILO,
     file = "Output/data_general.RDATA")
save(d_transcript,
     file = "Output/data_pillar_1.RDATA")
save(d_text,
     file = "Output/data_pillar_2.RDATA")
```

>>>>

# Save Data
```{r}
save(d_course, lists, d_AoD, d_assessment, d_ILO,
     file = "Output/data_general.RDATA")
save(d_transcript, d_course,
     file = "Output/data_pillar_1.RDATA")
save(d_text,
     file = "Output/data_pillar_2.RDATA")
```
